---
## Run with  Rscript -e "rmarkdown::render('file.Rmd')"
output:
  html_document:
      mathjax: NULL
---


```{r, engine = "python", echo = FALSE}
import matplotlib.pyplot as plt
plt.close("all")
import imageio

# Reading the apple
file  = "example_apple.png"
image = imageio.imread(file)

def convert(x, what):
    from copy import copy
    x = copy(x)
    r = x[:,:,0].flatten() / 255.
    g = x[:,:,1].flatten() / 255.
    b = x[:,:,2].flatten() / 255.

    from colorspace.colorlib import sRGB
    from colorspace import desaturate
    import numpy as np
    cols = sRGB(r, g, b)
    if what == "desaturate":
        cols = desaturate(cols)
    elif what == "Cconst":
        cols.to("HCL")
        C = cols.get("C")
        # Correcting Chroma
        C[np.where(np.logical_and(C > 10, cols.get("L") > 20))] = 40.
        cols.set(C = C)
        cols.to("sRGB")
    elif what == "Lconst":
        cols.to("HCL")
        L = cols.get("L")
        # Correcting Chroma
        cols.set(L = np.repeat(60, len(cols.get("L"))))
        cols.to("sRGB")
    elif what == "fakecolor":
        R = cols.get("R")
        G = cols.get("G")
        B = cols.get("B")
        cols.set(R = G, G = B, B = R)
    else:
        raise ValueError("don't know what to do for {:s}".format(what))

    # Write to image and return
    x[:,:,0] = cols.get("R").reshape(image.shape[0:2]) * 255.
    x[:,:,1] = cols.get("G").reshape(image.shape[0:2]) * 255.
    x[:,:,2] = cols.get("B").reshape(image.shape[0:2]) * 255.
    return x

# Create desaturated apple and a version with constant
# chroma. The last one is a rainbow thing.
image_desat = convert(image, "desaturate")
image_Cconst = convert(image, "Cconst")
image_Lconst = convert(image, "Lconst")
image_fakecolor = convert(image, "fakecolor")
```


```{r, engine = "python", echo = FALSE, fig = TRUE, fig.width = 3, fig.height = 2.8}
fig = plt.figure()
ax  = fig.add_subplot(111)
ax.imshow(image)
plt.axis("off")

plt.subplots_adjust(left = 0.02, right = 0.98, top = 0.98, bottom = 0.02)
plt.show()
```

The plot below shows the very same picture again but with modified color information.
The left apple has no color at all (the chroma of all pixels is set to 0),
the apple on the right hand side is blue instead of red - something which does not
exist in nature. However, our visual system is still capable of identifying the
object within a few hundreds of a second.

One reason is that our visual system is very efficient processing smallest
differences in luminance. Our retina consists of about 5 to 6 times more
cone than rod cells which are very sensitive to intensity of an object.
The rod cells, which are responsible to distinguish between different colors,
are much less common and only concentrated in a relatively small are in the center
of the retina and is used to add additional attributes to the objects we see.
However, large parts of the information is gathered via luminance.
Our brain converts the luminance information an impression of a shape of the object,
in this case "an apple". Even without color (left image) or with unnatural color
attributes (right image) we can still easily identify the apple. 
The color on top is used as an additional attribute to check if the apple
is mellow and sweet, bitter, or might even be poisonous but is not really
necessary identify the apple itself.


```{r, engine = "python", echo = FALSE, fig = TRUE, fig.width = 6, fig.height = 3.5}
fig = plt.figure()
ax  = fig.add_subplot(121)
ax.imshow(image_desat)
ax.axis("off")

ax  = fig.add_subplot(122)
ax.imshow(image_fakecolor)
plt.axis("off")
plt.show()
```

The next image shows the same apple again, but the luminance is set constant.
Thus, we have to classify the object solely based on the color and the colorfulness
which is rather tricky.


```{r, engine = "python", echo = FALSE, fig = TRUE, fig.width = 3, fig.height = 2.8}
fig = plt.figure()
ax  = fig.add_subplot(111)
ax.imshow(image_Lconst)
plt.axis("off")

plt.subplots_adjust(left = 0.02, right = 0.98, top = 0.98, bottom = 0.02)
plt.show()
```




