---
## Run with  Rscript -e "rmarkdown::render('file.Rmd')"
output:
  html_document:
      mathjax: NULL
---

Color Palettes
--------------

In the R `colorspace <https://cran.r-project.org/package=colorspace>`_ package
the palettes are functions returning a set of hex colors as a character list,
the default method how colors are used in R.

The python colorspace package does it slightly different. Palettes are objects
rather than functions which allow to retrieve lists of hex colors using the
``colors()`` method but also provide additiona methods which allow to use the
palettes for plotting in python.

```{r checkoutput, echo = FALSE, fig = FALSE}
checkoutput <- function(x, text) {
    if ( all(div == py$div) ) {
        cat(sprintf("<check class=\"Rpy allfine\">R/py: %s</check>\n",text))
    } else {
        cat(sprintf("<check class=\"Rpy failed\">R/py: %s</check>\n",text))
    }
}
```


### Comparing default color palettes

```{python, echo = FALSE, fig = FALSE}
# Loading colors
from colorspace import diverging_hcl, sequential_hcl, qualitative_hcl
div = diverging_hcl()(11)
seq = sequential_hcl()(11)
qual = qualitative_hcl()(11)
```


```{r, echo = FALSE, fig = FALSE}
# Loading the libs
library("colorspace")
library("reticulate")

# R Colors
div  <- diverging_hcl(11)
seq  <- sequential_hcl(11)
qual <- qualitative_hcl(11)

# Checkoutput
checkoutput(all(div  == py$div),  "Compare diverging_hcl")
checkoutput(all(seq  == py$seq),  "Compare sequential_hcl")
checkoutput(all(qual == py$qual), "Compare diverging_hcl")
```

### Color transformation

```{python pycolortransform, echo = FALSE, fig = FALSE}
# Loading colors
from colorspace import diverging_hcl
from colorspace.colorlib import hexcols
cols = hexcols(diverging_hcl()(11))
cols.to("HCL")
H = cols.get("H")
C = cols.get("C")
L = cols.get("L")
hex = cols()
```


```{r Rcolortransform, echo = FALSE, fig = FALSE}
# Loading the libs
library("colorspace")
library("reticulate")

# R Colors
div  <- diverging_hcl(11)
HCL  <- as(hex2RGB(div), "polarLUV")
hex  <- hex(as(HCL, "RGB"))

# Checkoutput
checkoutput(sum(coords(HCL[,"H"]) - py$H) < 0.01, "colortransform, hue dimension")
checkoutput(sum(coords(HCL[,"C"]) - py$C) < 0.01, "colortransform, chroma dimension")
checkoutput(sum(coords(HCL[,"L"]) - py$L) < 0.01, "colortransform, luminance dimension")
checkoutput(all(hex == py$hex), "colortransform, HCL -> hex")
```














