---
## Run with  Rscript -e "rmarkdown::render('file.Rmd')"
output:
  html_document:
      mathjax: NULL
---

Color Palettes
--------------

In R, the color palettes themselfes are functions returning a set
of hex colors as a character vector, the default method to use colors in R.

The python colorspace package it handling it slightly different. Palettes are
objects rather than functions and allow to retrieve lists of hex colors using
the ``colors()`` method or the default object call, but also provide additional
methods to inspect and/or manipulate the color palettes.

### In R

```{r, echo = TRUE, fig = TRUE, fig.height = .5, fig.width = 7}
# Loading the library
library("colorspace")
# Loading a set of 11 colors
colors <- diverging_hcl(11)
# Plotting a simple color map
par(mar = rep(0,4))
swatchplot(colors)
```

### In python

```{python, echo = TRUE, fig = TRUE, fig.height = .5, fig.width = 7}
# Loading the module
from colorspace import diverging_hcl, swatchplot
# Initialize the diverging_hcl object with default arguments,
# by default it is the "Blue-Red" diverging color palette.
pal    = diverging_hcl()
# Draw a set of 11 unique colors from the diverging palette.
colors = pal.colors(11)
# Plotting a simple color map
swatchplot(colors)
# Or simply:
pal.swatchplot(11)
```


Color Transformation
--------------------

Another difference between the _R_ and the _python_ implementation
is the way how colors are transformed between the different color
spaces.

While the _R_ colorspace packge provides a set of coercing functions ("`as`"),
the python color objects provide a method "`.as(...)`". "`.as(...)`" converts a
set of colors from one color space into another, even if we have to go trough a
set of intermid color spaces (e.g., from hex colors to HCL which goes from hex
to sRGB, RGB, CIE-XYZ, CIE-LUV, HCL). The example below shows how a set of hex
colors are transformed to HCL colors and back.


### In R

```{r, echo = TRUE, fig = TRUE, fig.height = .5, fig.width = 7}
# Loading the library
library("colorspace")
# Prepare a set of 5 colors from the default deverging_hcl palette
colors <- diverging_hcl(5)
print(colors)
# Convert to HCL
HCL <- as(hex2RGB(colors), "polarLUV")
print(HCL)
# Convert back to hex
colors <- hex(as(HCL, "RGB"))
print(colors)
```

### In python

```{python, echo = TRUE, fig = TRUE, fig.height = .5, fig.width = 7}
# Loading the module
from colorspace import diverging_hcl
# Prepare a set of 5 colors from the default diverging_hcl palette
colors = diverging_hcl()(5)
print(colors)
# Convert to HCL
from colorspace.colorlib import hexcols
colors = hexcols(colors)
colors.to("HCL")
print(colors)
# Getting hex colors again by either using the call method
# or transforming the object back to a "hexcols" object.
print(colors())
# Transform ...
colors.to("hex")
print(colors)
```






