---
## Run with  Rscript -e "rmarkdown::render('file.Rmd')"
output:
  html_document:
      mathjax: NULL
---

Create a new ``HCL`` color object with a set of
(manually specified) colors:

```{r, engine = "python", fig.width = 8, fig.height = 0.5}
from colorspace.colorlib import HCL

# Let's specify a set of HCL colors.
# These three colors are a bright blue (260, 100, 50),
# a neutral light gray (310, 0, 90) and a bright red (360, 100, 50)
# from the "Red-Blue 2" diverging color palette.
cols = HCL(H = [160, 210, 260, 310, 360],
           C = [ 70,  40,  10,  40,  70],
           L = [ 50,  70,  90,  70,  50])
cols.swatchplot()
```

```{r, engine = "python", fig.width = 7, fig.height = 0.5}
# Show current values, as "c" is a HCL object the method
# prints the H, C, L color coordinates.
print cols

# Following the image above we would like to do the following:
# (1) convert HCL to CIEXYZ,
cols.to("CIEXYZ")
print cols

# (2) convert CIEXYZ to sRGB,
cols.to("sRGB");      print cols

# (3) convert sRGB to hex colors,
cols.to("hex");       print cols

# (4) convert hex colors to RGB,
cols.to("RGB");       print cols

# (5) convert RGB to polarLAB,
cols.to("polarLAB");  print cols

# (6) and finally back to HCL.
cols.to("HCL");       print cols

# Plotting colors
cols.swatchplot()
```

As you can see the final object ``cols`` is, again, the one we have
specified at the beginning of the example - or at least mainly the
same. The small differences between the initial values and the
Hue-Chroma-Luminance values in our final object result from the
hex-transformation (to and from hex colors). Furthermore, for some
colors having low chroma and high luminance the identification of
the exact hue is not always unambiguous which can also yield
differences when transforming the colors back and forth.





