---
## Run with  Rscript -e "rmarkdown::render('file.Rmd')"
output:
  html_document:
      mathjax: NULL
---


```{r, engine = "python", echo = FALSE}
import matplotlib.pyplot as plt
plt.close("all")
import imageio

# Reading the apple
file  = "example_apple.png"
image = imageio.imread(file)

def convert(x, what):
    from copy import copy
    x = copy(x)
    r = x[:,:,0].flatten() / 255.
    g = x[:,:,1].flatten() / 255.
    b = x[:,:,2].flatten() / 255.

    from colorspace.colorlib import sRGB
    from colorspace import desaturate
    import numpy as np
    cols = sRGB(r, g, b)
    if what == "desaturate":
        cols = desaturate(cols)
    elif what == "Cconst":
        cols.to("HCL")
        C = cols.get("C")
        # Correcting Chroma
        C[np.where(np.logical_and(C > 10, cols.get("L") > 20))] = 40.
        cols.set(C = C)
        cols.to("sRGB")
    elif what == "Lconst":
        cols.to("HCL")
        L = cols.get("L")
        # Correcting Chroma
        cols.set(L = np.repeat(60, len(cols.get("L"))))
        cols.to("sRGB")
    elif what == "fakecolor":
        R = cols.get("R")
        G = cols.get("G")
        B = cols.get("B")
        cols.set(R = G, G = B, B = R)
    else:
        raise ValueError("don't know what to do for {:s}".format(what))

    # Write to image and return
    x[:,:,0] = cols.get("R").reshape(image.shape[0:2]) * 255.
    x[:,:,1] = cols.get("G").reshape(image.shape[0:2]) * 255.
    x[:,:,2] = cols.get("B").reshape(image.shape[0:2]) * 255.
    return x

# Create desaturated apple and a version with constant
# chroma. The last one is a rainbow thing.
image_desat = convert(image, "desaturate")
image_Cconst = convert(image, "Cconst")
image_Lconst = convert(image, "Lconst")
image_fakecolor = convert(image, "fakecolor")
```

As an example, the picture below shows a juicy and delicious apple.
Our visual system needs a fraction of second to identify the object.

```{r, engine = "python", echo = FALSE, fig = TRUE, fig.width = 3, fig.height = 2.8}
fig = plt.figure()
ax  = fig.add_subplot(111)
ax.imshow(image)
plt.axis("off")

plt.subplots_adjust(left = 0.02, right = 0.98, top = 0.98, bottom = 0.02)
plt.show()
```

The plot below shows the very same picture again but the color information has been
modified. The left apple has no color at all (the chroma of all pixels is set to 0),
the apple on the right hand side is blue instead of red - something which does not
exist in nature. However, it is still easy to identify the object as an apple.

One reason is that our visual system (eye-brain) is very efficient to identify
smallest changes in luminance (the lightness/darkness of a color). Our eye 
consists of different photo-reactive cells, so called cone cells and rod cells.
Three different types of cone cells allow our visual system to distinguish between
different colors and are only concentrated in a very small area in the center of our
retina. The rod cells are about 5 to 6 times more common and are placed on a larger
area around the center of our retina.
Rod cells are only sensitive to the intensity of light which allows us to identify
smallest differences in luminance.

The luminance information is gives us an impression of the shape of the object which
allows us to quickly identify an object. The luminance information in both images
below is maintained which makes it easy to identify the object.


```{r, engine = "python", echo = FALSE, fig = TRUE, fig.width = 6, fig.height = 3.5}
fig = plt.figure()
ax  = fig.add_subplot(121)
ax.imshow(image_desat)
ax.axis("off")

ax  = fig.add_subplot(122)
ax.imshow(image_fakecolor)
plt.axis("off")
plt.show()
```

The next image shows the same apple again, but the luminance is held constant.
Thus, it is getting very difficult to capture the actual shape of the object and
to extract the important information from the image.


```{r, engine = "python", echo = FALSE, fig = TRUE, fig.width = 3, fig.height = 2.8}
fig = plt.figure()
ax  = fig.add_subplot(111)
ax.imshow(image_Lconst)
plt.axis("off")

plt.subplots_adjust(left = 0.02, right = 0.98, top = 0.98, bottom = 0.02)
plt.show()
```




