---
## Run with  Rscript -e "rmarkdown::render('file.Rmd')"
output:
  html_document:
      mathjax: NULL
---


The `cvd_emulator` function provides a simple way to simulate
color vision deficiencies. 
For an existing pixel image (jpg/png/jpeg) simulations for
deuteranope, protanope, and tritanope color vision can be performed
with different severity levels.

The following plot shows a colorful figure on the left (original image)
followed by deuteranope sight and monochromatic sight.


```{r, engine = "python", echo = TRUE, fig.width = 8, fig.height = 2.8}
from colorspace import cvd_emulator
cvd_emulator(cvd = ['original','deutan','desaturate'], severity = 1)
```

The additional parameter allows to adjust the severity of the color
vision deficiency (`[0.-1.]`), here shown for an 80 percent deficiency
and deuteranope, protanope, and tritanope color vision.

```{r, engine = "python", echo = TRUE, fig.width = 8, fig.height = 2.8}
from colorspace.hcl_converter import hcl_converter
cvd_emulator(cvd = ['deutan', 'protan', 'tritan'], severity = .8)
```

Thanks to [@mariogogh](https://unsplash.com/@mariogogh) on
[unsplash.com](https://unsplash.com) for the colorful picture. By the way,
the bird is used to trace the handling of RGBA values.
